Size-differentiated Export in different Dynamical Regimes in the Ocean

### 2019-06-22 size_differentiated_export.tex
Updates from Overleaf

%FIG6
\begin{figure}[ht!]
	\centering
	%\includegraphics[width = 1\linewidth]{figures/Fig6_particle_export_flux.png}
	%\caption{Upward (top) and downward (bottom) fluxes of particles (thin lines) at the 100 m depth horizon as a function of time in \textit{Papa\_summer} (left), and \textit{Papa\_winter} (right). Fluxes are normalized by the total amount of particles (N = 1,971,717), daily-averaged and integrated over the entire domain. For each sinking-velocity class, the net particle flux is shown by a thick line. Expected downward fluxes based on only gravitational sinking are indicated with dashed lines in the left panels.}
	\includegraphics[width = 1\linewidth]{figures/Fig6.png}
	\caption{[left] Gridded anomaly in the median depth of particles 25 days after particle release, in the Winter experiment. Blue (red) grid cells indicate that the median depth of particles in this cell is deeper (shallower) than expected based on a 1D gravitational model where $z = w_s\timest$. [right] Probability Distribution Function (PDF) of particles as a function of depth for each velocity class. The winter distribution is shown as thick lines, while the summer distribution is represented by the shaded regions. Triangle markers indicate the expected depth of particles after 25 days based on the 1D gravitational model, which is used as a reference to compute the depth anomalies. Release depth is indicated by the thick dashed line.}	
	\label{fig: particle_depth_distribution}
\end{figure}

@@

 \fixme{main points of new figure 8:
\begin{itemize}
    \item The impact of remineralization is three-fold: (1) it affects the total amount of biomass, as biomass is slowly remineralized - as illustrated by the decrease in area below the curves. (2) It shifts the PDFs of relative biomass as a function of vertical velocity towards slower vertical velocities. that is because, as they remineralize, the particles slow down. This has less of an impact on slower-sinking particles, as they are already sinking slowly anyway, so their PDFs don't change much, and the resulting downward biomass flux remains relatively large. faster-sinking particles, however, are more affected by the remineralization process, as their total vertical velocity shifts from gravitationally driven to advectively driven. as a result, their associated downward relative biomass flux is greatly decreased. Slow-sinking particles dominate the downward relative flux of biomass in both the summer and winter in the presence of remineralzation, as opposed to just the summer when remineralization is not included.
\end{itemize}
}

>>>>

%FIG6
\begin{figure}[ht!]
	\centering
	%\includegraphics[width = 1\linewidth]{figures/Fig6_particle_export_flux.png}
	%\caption{Upward (top) and downward (bottom) fluxes of particles (thin lines) at the 100 m depth horizon as a function of time in \textit{Papa\_summer} (left), and \textit{Papa\_winter} (right). Fluxes are normalized by the total amount of particles (N = 1,971,717), daily-averaged and integrated over the entire domain. For each sinking-velocity class, the net particle flux is shown by a thick line. Expected downward fluxes based on only gravitational sinking are indicated with dashed lines in the left panels.}
	\includegraphics[width = .8\linewidth]{figures/Fig6.png}
	\caption{[left] Gridded anomaly in the median depth of particles 25 days after particle release, in the Winter experiment. Blue (red) grid cells indicate that the median depth of particles in this cell is deeper (shallower) than expected based on a 1D gravitational model where $z = w_s\timest$. [right] Probability Distribution Function (PDF) of particles as a function of depth for each velocity class. The winter distribution is shown as thick lines, while the summer distribution is represented by the shaded regions. Triangle markers indicate the expected depth of particles after 25 days based on the 1D gravitational model, which is used as a reference to compute the depth anomalies. Release depth is indicated by the thick dashed line.}	
	\label{fig: particle_depth_distribution}
\end{figure}

@@
